Towards Reliable Machine Learning Deployments in the Cloud

### 2024-03-28 plots/combined/aft_comparison.tex
update plots

\begin{table}
\caption{Comparison of AFR Models on the COMBINED dataset.}
\label{tab:Combined}
\begin{tabular}{llrlrr}
\toprule
 & AIC & Concordance & BIC & Mean $S(t;\theta)$ & Median $S(t;\theta)$ \\
\midrule
weibull & -4732.34 & 0.82 & -4732.34 & 0.00 & 0.00 \\
cox & -- & 0.82 & -- & 0.00 & 0.00 \\
log_logistic & -4770.78 & 0.81 & -4770.78 & 0.00 & 0.00 \\
log_normal & -4788.03 & 0.81 & -4788.03 & 0.00 & 0.00 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{Comparison of AFR Models on the COMBINED dataset.}
\label{tab:Combined}
\begin{tabular}{lrrrrrr}
\toprule
 & AIC & Concordance for $x_t$ & Concordance for $x_i$ & BIC & Mean $S(t;\theta|x_{t})$ & Mean $S(t;\theta|x_{i})$ \\
\midrule
weibull & -5810.78 & 0.84 & 0.84 & -5810.78 & 2.08 & 0.65 \\
log_logistic & -6204.80 & 0.85 & 0.84 & -6204.80 & 0.23 & 0.17 \\
log_normal & -6076.91 & 0.84 & 0.84 & -6076.91 & 0.17 & 0.15 \\
\bottomrule
\end{tabular}
\end{table}
